Prefix-free graphs and suffix array construction in sublinear space

### 2023-06-26 manuscript/content/01_introduction.tex
moved content to content

A suffix array is a data structure from the stringology field with a massive impact on designing many efficient algorithms on strings.
Particularly in bioinformatics, it is responsible for the design of such data structures as the Burrows-Wheeler transform \cite{burrows1994block} or FM-index \cite{ferragina2000opportunistic}, which in turn allowed for efficient mapping of reads to the reference and several other fundamental bioinformatics operations.
These fundamental operations are well-studied on sequential data, but the recent paradigm shift of moving from a single reference genome to a graph pangenome made it even more complicated to apply the acquired knowledge from the stringology field to biological sequences.

>>>>

A suffix array is a data structure from the stringology field with a massive impact on designing many efficient algorithms on strings.
Particularly in bioinformatics, it is responsible for the design of such data structures as the Burrows-Wheeler transform \cite{burrows1994block} and FM-index \cite{ferragina2000opportunistic}, which in turn allowed for efficient mapping of reads to the reference and several other fundamental bioinformatics operations.
These fundamental operations are well-studied on sequential data, but the recent paradigm shift of moving from a single reference genome to a graph pangenome made it even more complicated to apply the acquired knowledge from the stringology field to biological sequences.
